Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data

### 2022-12-01 analysis/TAS_memo/memo_TAS_reviewers.Rmd
Update memo_TAS_reviewers.Rmd

This comment is not clear to us. The real data analyses are based on real _historical_ trial data from the stae of Connecticut (see lines x to y). Users of the app have the option to run the models excluding any historical trial data (as suggested by the comment) by not selecting the name of a prosecutor or defense attorney. In this case the normal(0,2) prior is used for the bias parameter. Similarly, the app gives the user the option of altering the weight the historical strike data (if selected) by adjusting alpha (power prior parameter). Thus the user can: 1) choose not to use historical data, 2) use historical data with equal weight as the current trial (alpha = 1), or 3) down-weight the historical trial data.

@@

[INSERT] We agree. Although, unfortunately this additional information (age, etc) is not routinely collected by the courts, and therefore is difficult to consider in the context of our model. We have added a sentence (line x) to the discussion that highlights this point by calling for the need to reassess how, and more importantly what, information is collected on prospective jurors, so that models like ours can be used to my the process more fair and equittable.

@@

>>>>

This comment is not clear to us. The real data analyses are based on real _historical_ trial data from the state of Connecticut (see lines x to y). Users of the app have the option to run the models excluding any historical trial data (as suggested by the comment) by not selecting the name of a prosecutor or defense attorney. In this case the normal(0,2) prior is used for the bias parameter. Similarly, the app gives the user the option of altering the weight the historical strike data (if selected) by adjusting alpha (power prior parameter). Thus the user can: 1) choose not to use historical data, 2) use historical data with equal weight as the current trial (alpha = 1), or 3) down-weight the historical trial data.

@@

[INSERT] Batson challenge doesn't care if you strike a cognizable class because you assume they have particular confounders (e.g., low income, etc). [editme] We do explicitly highlight that trial-level characteristics and impact compatibility between current and historical trials. We do advocate for reassessment of the way (and what) data are collected from individual trials.

@@

[INSERT] Choose it based on beliefs on causes of incompatibility and evaluate bias detections sensitivity to its value.
